\begin{thebibliography}{99}
  
  \bibitem{tensor_alg_and_rep} 池田 岳　(2022). テンソル代数と表現論: 線型代数続論　東京大学出版会.
  \bibitem{enu_geo} 池田 岳　(2018). 数え上げ幾何学講義: シューベルト・カルキュラス入門　東京大学出版会.
  \bibitem{alg_2} 雪江 明彦　(2010). 代数学2 環と体とガロア理論 (代数学シリーズ).
  \bibitem{alg_intro} 堀田 良之　(2021). 代数入門(新装版): 群と加群 (数学シリーズ) 裳華房.
  \bibitem{homological} 岩永 恭雄・佐藤 眞久 (2002). 環と加群のホモロジー代数的理論 日本評論社.
  \bibitem{young_tableau} Fulton,W. (1996). \textit{Young tableaux:with applications to representation theory and geometry.} Cambridge University Press. (W.フルトン　 池田 岳・井上 玲・岩尾 慎介(訳) (2019). ヤング・タブロー:表現論と幾何への応用　丸善出版).
  \bibitem{serre} Serre,J.P. (1977). \textit{Linear representation of finite group.} Springer. (J.P.セール　岩堀 長慶・横沼 健雄(訳) (2019). 有限群の線形表現　岩波書店).
  \bibitem{AM} Atiyah,M.F., \& MacDonald,I.G. (1969). \textit{Introduction to commutative algebra.} Westview Press. (M.F.アティヤ・I.G.マクドナルド　新妻 弘(訳) (2006). 可換代数入門　共立出版).
  \bibitem{fulton_harris} Fulton,W., \& Harris,J. (2004). \textit{Representation theory: a first course.} Springer. 
  \bibitem{adv_alg}Knapp,A.W. (2007). \textit{Advanced algebra} Birkhauser Boston.
  \bibitem{macdonald} MacDonald,I.G. (1995). \textit{Symmetric functions and hall polynomials second edition.}  Oxford University Press Inc., New York.
  \bibitem{sym_func} Stanley,R.P. (2010). \textit{Enumerative combinatorics volume 2.} Cambridge University Press
  \bibitem{RH} Hartshorn,R. (1977). \textit{Algebraic geometry.} Springer.
  \bibitem{FA} Fulton,W. (1974). \textit{Algebraic curves.} Addison Wesley Publishing Company. 
  \bibitem{HA} Harris,J. (1992). \textit{Algebraic geometry a first course.} Springer
  \bibitem{3264}Eisenbud, D., \& Harris, J. (2016). \textit{3264 and All That: A Second Course in Algebraic Geometry. }Cambridge: Cambridge University Press. 
  \bibitem{knuth} Knuth,D. (1970). Permutations, matrices, and generalized young tableaux. \textit{Pacific Journal of Mathematics, }Vol. 34, No. 3.
\end{thebibliography}